Stay in shape! Homework exam II

### 2016-03-15 geometricAlgorithms/homeworkExam/2/homeworkExam.tex
1a

		There exists some half plan whose's area never crosses the x axis
		(so is either completly above or below y=0).
	\item \emph{There are arbitrarly large disk with the specifications.}

		The half planes do not enclose the disk area.
	\item \emph{The largest disk exists and is unique.}

	\item \emph{There are several equally large largest disks}
\end{enumerate}
\subsection{Deal with case ii in linear worstcase time}
\subsection{Formulate and proof the RIC lemma}
\subsection{Give the RIC algorithm}
\subsection{Prove the expected running time}
% Don't forget to remove constants
\subsection{Eplain why you can't use RIC for points}
\section{A datastructure for horizontal line segments}
\subsection{Analyze the storage requirements}
\subsection{Argue that all horizontal line segs are found}
\subsection{Give psuedo code for the query algorithm}
\subsection{Analyze the query time}
\section{Voronoi nearest neigbour\emph{s}}
%TODO: wtf? maybe with higher order voronoi?? But it won't be log n
\end{document}

>>>>

		The intersection of halfplanes of $H$ never crosses the x axis,
		so it exists entirely above or below $y=0$.

	\item \emph{There are arbitrarly large disk with the specifications.}

		The intersection of halfplanes of $H$ do not enclose the disk
		area.
		In fact the area they do enclose is smaller than $\pi$ radials.

	\item \emph{The largest disk exists and is unique.}

		The intersection of halfplanes of $H$ produces an area with no
		parralel lines.

	\item \emph{There are several equally large largest disks}

		The intersection of halfplanes of $H$ produces an area with
		parralel lines.

\end{enumerate}

\subsection{Deal with case ii in linear worstcase time}
throw new exception(``done'');
\subsection{Formulate and proof the RIC lemma}
\subsection{Give the RIC algorithm}
\subsection{Prove the expected running time}
% Don't forget to remove constants
\subsection{Eplain why you can't use RIC for points}
\section{A datastructure for horizontal line segments}
\subsection{Analyze the storage requirements}
\subsection{Argue that all horizontal line segs are found}
\subsection{Give psuedo code for the query algorithm}
\subsection{Analyze the query time}
\section{Voronoi nearest neigbour\emph{s}}
%TODO: wtf? maybe with higher order voronoi?? But it won't be log n
\end{document}
